### 2023-06-15 introduction.tex
up

\begin{center}
	\begin{figure}
			\hspace{0.74cm}
\includegraphics[width=0.87\textwidth]{FigureB}
	\caption{A lossy VASS with three subsystems and four counters. Leftmost and rightmost systems $A$ and $B$ represents aircrafts attempting to land and staying on stand-by in the air while they haven't received permission to land, while the middle one $M$ represent the control tower managing the aircrafts landings so that only one aircraft at a time is allowed for landing.}
					\label{air control}
	\end{figure}
\end{center}

\begin{example}\label{Example}
Consider the vector addition system in Figure~\ref{air control}. It models a scenario in which two aircrafts wants to land in an airport at the same time. 
The automata $A$ on the left and $B$ on the right represent the aircrafts attempting to land, while the middle one $M$ represents the control tower. The control tower can communicate information to the aircrafts using 
% channels $c_1$ and $c_2$, and these in turn can send messages to the control tower using 
the first two shared counters, and these in turn can send messages to the control tower
using the last two shared counters. 
% respectively channel $c_3$ and $c_4$. 
% Remark channels $c_3$ and $c_4$ have a unary alphabet in the exemple and therefore can be seen as counters.

Safety requires that only one aircraft at a time attempt to land. The role of the control tower is to ensure this;
there are two possible choices: aircraft $A$ waits for aircraft $B$ to land
or vice-versa. To make its choice known to the aircrafts, the control tower will use the counters. 
We assume that the VASS is
lossy \-- i.e. 
 the contents of a counter can spontaneously get lower at any time
 \--  but that they are still such that out of ten incrementations of a counter, at least one is not rendered void.
In this example, the safe, desirable state would be one where the aircrafts have both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,5}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4\}$, and $\Bad$ is the complement of $\Safe$. 
% We remark that $\Safe$ and $\Bad$ are here both upward and downward closed.
Resilience here expresses that the aircrafts will both land, while explicit resilience or $k$-resilience asks whether they will do so in at most $k$ steps. 
Explicit resilience is of interest since in general we want to ensure the safe space will
be reached in
the least amount of steps possible. 
In this exemple, for instance, aircrafts cannot simply wait in the air an infinite amount of time.
With one out of ten increment of a counter guarranteed to not be lost, $40$-resilience hold in the example.
\end{example}

>>>>

\begin{center}
	\begin{figure}
			\hspace{0.74cm}
\includegraphics[width=0.87\textwidth]{FigureB}
	\caption{A lossy VASS with three subsystems and four counters. Leftmost and rightmost systems $A$ and $B$ represent aircrafts attempting to land and staying on stand-by in the air while they haven't received permission to land, while the middle one $M$ represents the control tower managing the aircrafts landings so that only one aircraft at a time is allowed for landing.}
					\label{air control}
	\end{figure}
\end{center}

\begin{example}\label{Example}
Consider the vector addition system in Figure~\ref{air control}. It models a scenario in which two aircrafts want to land in an airport at the same time. 
The automata $A$ on the left and $B$ on the right represent the aircrafts attempting to land, while the middle one $M$ represents the control tower. The control tower can communicate information to the aircrafts using 
% channels $c_1$ and $c_2$, and these in turn can send messages to the control tower using 
the first two shared counters, and these in turn can send messages to the control tower
using the last two shared counters. 
% respectively channel $c_3$ and $c_4$. 
% Remark channels $c_3$ and $c_4$ have a unary alphabet in the exemple and therefore can be seen as counters.

Safety requires that only one aircraft at a time attempts to land. The role of the control tower is to ensure this;
there are two possible choices: aircraft $A$ waits for aircraft $B$ to land
or vice-versa. To make its choice known to the aircrafts, the control tower will use the counters. 
We assume that the VASS is
lossy \-- i.e. 
 the contents of a counter can spontaneously get lower at any time
 \--  but that they are still such that out of ten incrementations of a counter, at least one is not rendered void.
In this example, the safe, desirable state would be one where the aircrafts have both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,5}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4\}$, and $\Bad$ is the complement of $\Safe$. 
% We remark that $\Safe$ and $\Bad$ are here both upward and downward closed.
Resilience here expresses that the aircrafts will both land, while explicit resilience or $k$-resilience asks whether they will do so in at most $k$ steps. 
Explicit resilience is of interest since in general we want to ensure the safe space will
be reached in
the least amount of steps possible. 
In this exemple, for instance, aircrafts cannot simply wait in the air an infinite amount of time.
With one out of ten increment of a counter guarranteed to not be lost, $40$-resilience hold in the example.
\end{example}
